% ------
% Career
% ------
\section{Career}

\mySubHeadingListStart


  \mySubHeading
  {Ground Integration Engineer}{Nov 2023 -- Present}
  {\faIcon{building} NASA, National Aeronautics and Space Administration
  }{Kennedy Space Center, FL, USA}
    \myItemListStart
      \myItem{Developed a PowerShell script for automation of auditing requirement traceability in JAMA.}
      \myItem{Guided subsystem teams in crafting comprehensive requirement closure plans.}
      \myItem{Designed and tailored new and existing DVOs to meet emerging Program needs.}
      \myItem{Enhanced requirement traceability by teaming up with subsystem experts to improve clarity and consistency in ICDs and system specifications.}
    \myItemListEnd

  \mySubHeading
  {Pre-Feature Owner}{Sep 2022 -- Jul 2023}
  {\faIcon{building} Ford Motor Company}{Dearborn, MI, USA}
    \myItemListStart
      \myItem{Developed HARA, FMEA, specifications, requirements, and other documentation for future EV features.}
      \myItem{Led a team of 10 internal stakeholders to develop a EV powertrain feature from ideation to development ready in 6 months.}
      \myItem{Developed an AI/ML feature from ideation to production ready.}
      \myItem{Used MagicDraw for modeling and simulation of  3 future features.}
    \myItemListEnd

  \mySubHeading
  {V2X Feature Development and Innovation Engineer}{Feb 2022 -- Sep 2022}
  {\faIcon{building} Ford Motor Company}{Dearborn, MI, USA}
    \myItemListStart
      \myItem{Ideated and developed new features in Stationary Moments and Commercial Electrification.}
      \myItem{Researched and scoped future features implementing blockchain technology.}
      \myItem{Filled in as Product Manager for Public Charging Team while role was back filled.}
    \myItemListEnd

  \mySubHeading
  {Autonomous Driving Development Intern}{May 2021 -- Aug 2021}
  {\faIcon{building} HATCI, Hyundai Kia America Technical Center, Inc.}{Ypsilanti, MI, USA}
    \myItemListStart
      \myItem{Validated embedded controls for V2X (Vehicle to Everything Communication) pilot project.}
      \myItem{Developed python scripts for testing of V2X applications without Road Side Units.}
      \myItem{Created documentation and test plans for five new V2X applications.}
      \myItem{Assisted with ADAS benchmarking of competitor vehicles.}
    \myItemListEnd

  \mySubHeading
  {Electrical Engineering Intern}{May 2019 -- Aug 2019}
  {\faIcon{building} The Wooster Brush Company}{Wooster, OH, USA}
    \myItemListStart
      \myItem{Updated schematics of six legacy machines with safety critical improvements.}
      \myItem{Troubleshot software incorporating sensors, computer vision, and robots.}
    \myItemListEnd

\mySubHeadingListEnd
